---
title: "Weight of Fish"
author: "Sakana Uthayasegar"
date: "July 31, 2023"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

# Predicting Fish Weight
## get data
```{r}
fishData=read.csv("Fish.csv")
```


## Perch
```{r}
perch = filter(fishData, Species == "Perch")
```

### Best Models
```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=perch,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```
The best two variables that ca be used to predict weight are height and width. 

### Best Two regressor model

```{r}
perchModel=lm(Weight~Height+Width,data=perch)
summary(perchModel)


## Pike

```{r}
pike = filter(fishData, Species == "Pike")
```
The best model has the adjusted r squared of 0.94

### Best Models
```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=pike,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)



### Best Two regressor model
```


```{r}
perchModel=lm(Weight~Length1+Length3,data=pike)
summary(perchModel)
```
The best model for the adjusted R squared is 0.9649


## Roach

```{r}
Roach = filter(fishData, Species == "Roach")
```

### Best Models

```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=Roach,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```
The two best variables for Roach is Length 3 and Width.

### Best Two regressor model

```{r}
RoachModel=lm(Weight~Length3+Width,data=Roach)
summary(RoachModel)
```
The adjusted R squared is 0.8482

## Final Summary Statements

Analyzing the data from lowest to highest adjusted R squared, based on that reports, Roach would be the lowest, second is Perch. Finally, the best is Pike with the highest adjusted R squared of 0.96. 

